---
title: "Mapping Problem"
author: "David Kane"
date: "3/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(sf)
library(tidyverse)
```

The purpose of this document is to highlight a mapping problem that is making me crazy.

```{r}
# This is a collection of notes for working with data from the Stanford Open
# Policing Project. 

# https://openpolicing.stanford.edu/

# Looks like the best data to work with is from Hartford.

orig <- read_rds("~/Downloads/tr137st9964_ct_hartford_2019_02_25.rds") 

# read_sf() is an alias, but it is a good alias.

shapes <- read_sf("~/Downloads/ct_hartford_shapefiles/Hartford_Neighborhoods.shp")

```

```{r}
points <- orig %>% sample_n(10)

ggplot(data = shapes) + 
  geom_sf() +
  geom_point(data = points, aes(y = lat, x = lng)) 
  # coord_sf(xlim = c(-72.7, -72.6), ylim = c(41.7, 41.85), expand = FALSE)
```

## location

Location provides a pretty good street address. 

What are the most popular stop locations?

What street features the most stops? 

What street number?

How many stops in each type of road?

## time

There are interesting patterns by time. No stops in the arly AM. No stops at lunch.

## lat and lng

Are there outliers?

## district provides a nice faceting option.

## officer_id_hash

Some officers have a lot more stops than other officers!

## arrest_made, citation_issued and warning_issued

Looking at this seems useful. Conditional on a stop, what influences likelihood of arrest? Or citation? Does everything end with one of these three things? Not exactly. See the outcome variable.

## search variables are confusing

## reason_for_stop us very interesting


