---
title: "Policing in Hartford"
author: "David Kane"
date: "3/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(fs)
library(sf)
library(tidyverse)
```

For understanding mapping in R, start with [Chapter 7](http://socviz.co/maps.html#maps) in Healy. Then, because Healy does not use simple features (sf), the best modern approach to mapping, you should review [this three part tutorial](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf.html).

I am using data from the [Stanford Open Policing Project](https://openpolicing.stanford.edu/). Toward [the middle of this page](https://openpolicing.stanford.edu/data/) is the data for Hartford. 




It is straightforward to make a map of Hartford:

```{r}
# Need two data sets. An RDS file with the traffic stops information and a shape
# file for the city of Hartford.

orig <- read_rds(url("https://stacks.stanford.edu/file/druid:tr137st9964/tr137st9964_ct_hartford_2019_02_25.rds")) 

# The shape files are tarred up, so we download them, unzip, load and then
# delete. read_sf() is an alias, but it is a good alias. I wish there were a
# cleaner way of doing these 4 steps . . .

download.file("https://stacks.stanford.edu/file/druid:tr137st9964/tr137st9964_ct_hartford_shapefiles_2019_02_25.tgz", destfile = "shapes.tgz")

untar("shapes.tgz")

shapes <- read_sf("ct_hartford_shapefiles/Hartford_Neighborhoods.shp")

file_delete(c("shapes.tgz", "ct_hartford_shapefiles/"))

# It is now easy to make a simple map of Hartford.

ggplot(data = shapes) + 
  geom_sf()

```

Note that Hartford is a relatively small city, with 0.1 of width/length in terms of longitude and lattitude. Fortunately, our data seems much more precise than that.


```{r}
set.seed(9)
points <- orig %>% 
  select(district, location, lat, lng, subject_race) %>% 
  drop_na(lng, lat) %>% 
  sample_n(100)
```

I just want to plot those 10 points on my map. I have a map and we have some points with appropriate latitude and longitude. The trick is that you want the points to be a special kind of object. Once it is, you can just use it with `geom_sf`. The answer was in that three part tutorial. Just needed to read it!

```{r, echo=TRUE}

sites <- st_as_sf(points, coords = c("lng", "lat"), crs = 4326)

ggplot(data = shapes) +
  geom_sf() +
  geom_sf(data = sites, size = 0.1, aes(color = subject_race))

```



